Mega-analysis of the Interoceptive Accuracy Scale (IAS)

### 2025-08-29 analysis/Study1.qmd
updated study 1 html

- Makowski
  - Note: First sample has some missing items (No Taste, Cough, Blood_Sugar)
  - Note: Analog scales

@@

- Poreiro et al., 
  - Study 1: https://osf.io/49wbv

@@

### Sample 15
- Poreiro: unpublished

@@

- Raquel Arjona and Robyn Scharte data

>>>>

- Makowski
  - Note: sample has some missing items (No Taste, Cough, Blood_Sugar)
  - Note: Analog scales

@@

- Poerio et al., 
  - Study 1: https://osf.io/49wbv

@@

### Sample 15
- Poerio: unpublished

@@

- Raquel Arjona and Robyn Scharte data upublished
